The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-12 paper/iphas-dr2.tex
More tidying
-

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
%\usepackage{lscape}
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}

@@

\author[G. Barentsen
et. al]{G. Barentsen$^{1}$\thanks{E-mail:geert@barentsen.be},
H. J. Farnhill$^{1}$,
J. E. Drew$^{1}$,
M. J. Irwin$^{4}$, \newauthor
E. A. Gonz$\acute{\rm{a}}$lez-Solares$^{4}$,
R. Greimel$^{2}$,
B. Mizalski$^{3}$,
C. Ruhland$^{1}$, \newauthor plus many friends.
\newauthor\\
$^{1}$Centre for Astrophysics Research, STRI, University of Hertfordshire, College Lane Campus, Hatfield AL10 9AB\\
$^{2}$Institute for Geophysics, Astrophysics and Meteorology, Institute of Physics, Karl-Franzens-Universit$\ddot{a}$t Graz, Universit$\ddot{a}$tsplatz 5, 8010 Graz, Austria\\
$^{3}$Building, Institute, Street Address, City, Code, Country\\
$^{4}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA}

@@

\begin{abstract} % BACKGROUND, OBJECTIVE, METHODS, RESULTS, CONCLUSIONS
The INT/WFC Photometric H$\alpha$ Survey 
of the Northern Galactic Plane (IPHAS)
is a 1800 deg$^2$ imaging survey
covering the entire northern Milky Way at $|b| < 5^\circ$
in the $r$, $i$ and \ha\ filters 
using the Wide Field Camera (WFC) 
on the 2.5-meter Isaac Newton Telescope (INT).
This data release presents the first 
uniformly-calibrated source catalogue
to have been extracted from the survey,
providing single-epoch photometry
for 219 million unique sources
across 92\% of the survey.
The observations were carried out between 2003 and 2012
at a median seeing of 1.1 arcsec
to a depth of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$ and \ha$=20.3\pm 0.3$
($5\sigma$ limits, Vega system).
We explain the data reduction 
and quality control procedures,
describe and test the new uniform photometric calibration,
and detail the construction of the source catalogue
and its quality warning flags.
We find that the new calibration is accurate to
$\sigma=0.03$ mag.
Finally, we demonstrate the ability of the 
catalogue's unique
$r$-$i$/$r$-\ha\ colour-colour diagram to
(i) characterise stellar populations and extinction regimes
towards different Galactic sightlines
and (ii) select reliable candidate \ha-emission line objects.
The catalogue which accompanies this paper
provides the much-needed visible-light counterpart
to several infrared surveys of the Galactic Plane,
including many poorly-studied star-forming regions and ``bubbles'',
and provides images for some of the most
crowded regions to be faced by Gaia.
\end{abstract}

@@

The mean source density as a function of Galactic longitude
is shown in Figure~\ref{fig:density} (thick blue line).
The densities were computed by counting the 
number of sources in $1^\circ$-wide longitude bins
across which covered the entire latitude range $-5^\circ<b<+5^\circ$.
Unsurprisingly, we find the average source densities to increase
towards the Galactic centre.
For example, the average source density near $l\simeq 30^\circ$
is roughly 30\,000 objects per square degree,
which is five times more than the density
found near $l\simeq 180^\circ$.

In addition to the global trend, 
there are significant variations in the source density on smaller scales.
For example,  we find a significant drop near the constellations 
of Cygnus ($l\simeq 80$) and Aquila ($l\simeq 40$),
which are regions known to be affected
by high levels of foreground extinction.
Dark clouds are visible towards these constellation by eye,
and they are often referred to as ``the Great Rift''.

We warn however that the densities reported here 
have not been corrected for survey completeness
or differences in the observing conditions across the survey.
For example, the dip in the density near $l\simeq140^\circ$
is an artificial feature caused by gaps
in the footprint coverage (which are apparent in Fig.~\ref{fig:footprint}).
In a forthcoming paper,
we aim to calibrate the IPHAS-based source densities
by injecting artificial stars into the IPHAS images
and measuring their recovery rate (Farnhill et al., in preparation).
Indeed IPHAS has the potential to offer
calibrated, two-dimensional stellar density maps
which can be used to constrain detailed models of our Galaxy,
but it is beyond the scope of the present work.

@@

In Figure~\ref{fig:density} we also shows the density
of non-blended sources (thin red line).
These are sources for which the \emph{deblend} flag is {\sc false},
i.e. sources for which the CASU pipeline did not have to apply 
a deblending procedure to separate the flux
originating from two or more overlapping objects.
We find a strong correlation between the source density
and the fraction of sources affected by source blending.
For example, only NN\% of the sources are blended
at $l>90^\circ$, whereas NN\% are blended at $l<90^\circ$.

As we explained earlier, blended sources must be used with caution.
Firstly, the deblending-procedure crucially depends
on the local PSF being measured accurately. 
Secondly, blended sources may are likely candidates to have fallen victim
to source confusion during the band-merging procedure.
In future work we hope to investigate the use of
more advanced PSF-fitting routines
in which sources are measured simultaneously across all bands,
perhaps guided by an external list of sources provided
by near-infrared surveys or Gaia data.

Each of the sightlines reveals a stellar population
with distinct characteristics.
Firstly, towards the Galactic anti-centre at $l=180^\circ$ (Fig.~\ref{fig:l180}) 
we find a population dominated by lowly-reddened main sequence stars.
This is consistent with the estimated total sightline extinction of $E(B-V)=0.49$
given by \cite{Schlegel1998}, following the correction of \cite{Schlafly2011}.
Looking in more detail we can see that the stellar locus is narrower for M-type dwarfs than for earlier types;
we do not observe M dwarfs experiencing the strongest reddening possible for this sightline.
This implies that extinction is still increasing at distances beyond $\sim 2$~kpc,
where M dwarfs are too faint to be contained in the IPHAS catalogue.
It is also clear that there are no unreddened stars earlier than $\sim$K0 visible,
such stars would be saturated if within a few hundred parsecs.
This therefore suggests that there is a measurable increase in extinction locally.
We also note an relative absence of late type giants which,
due to the relative brevity of the corresponding phase of stellar evolution,
would only account for a small proportion of a volume limited sample.

In contrast, 
closer towards the galactic centre at $l=45^{\circ}$ (Fig.~\ref{fig:l45}) we find a wealth of reddened objects.
In the colour-magnitude diagram it is clear that the stars are split into two distinct groups,
with one significantly redder than the other.
The bluer group is composed of main sequence stars,
with the slope of this group in the colour-magnitude diagram attributable to the significantly increasing extinction.
Meanwhile the redder group is principally composed of red giant stars.
As these stars are intrinsically brighter,
at some given apparent magnitude they will be substantially further away than their main sequence counterparts.
Given that, along this sight-line,
extinction continues to increase with distance,
the red giants we observe will be subject to more reddening than a main sequence star exhibiting the same apparent magnitude.
Therefore, the clear split between the two groups arises due to the combination of increasing extinction and the distinct absolute magnitude ranges of main sequence and giant branch stars.

Finally, in one of our earliest sightlines at $l=30^{\circ}$
we find a very high number of extremely reddened giants
in addition to an unreddened population
of foreground dwarfs.
In contrast to the sightline at $l=45^{\circ}$,
there is no clear group of giant stars visible in the colour-magnitude diagram of Fig.~\ref{fig:l30},
though the red clump stars are manifested as a slight over density which sits roughly 0.4~mags redder than the A0V reddening track.
At $(l,b)=(45^{\circ}, 2^{\circ})$ the giant stars observed exhibit a relatively narrow range of reddenings as the lie beyond most or essentially all of the Galactic dust.
At $(l,b)=(30^{\circ}, 0^{\circ})$ this is not the case:
even at the substantial distances at which we can observe reddened giant stars extinction is continuing to rise and we still find ourselves well within the Galactic dust disc.
It is also apparent that the $(r-i)$ width of both the M dwarfs and early A dwarfs is greater than that in Fig.~\ref{fig:l45}.
This is indicative of a steeper rise in reddening,
both within several hundred parsecs (M dwarfs)
and within a few kpc (early A dwarfs).

Here we have presented only a short qualitative description of the information obtainable from IPHAS colour-colour and colour-magnitude plots.
A more rigorous quantitative analysis of the IPHAS catalogue
can be undertaken to estimate both the stellar density distribution in the Milky Way \citep{Sale2010}
and to create detailed three-dimensional maps of the extinction across several kpc \citep{Sale2009,Sale2012}.
An extinction map based on our catalogue is to be released in a separate paper
that accompanies this data release (Sale et al., in preparation).

\begin{figure*}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-180-3.pdf} 
        \includegraphics[width=0.5\textwidth]{./plots/cmd-180-3.pdf}
    \end{minipage}
    \caption{Colour-colour and colour-magnitude diagram (left and right panel)
    showing sources flagged as \emph{veryReliable}
    located in an area of one square degree
    centred near the Galactic anti-centre 
    at $(l,b)=(180^\circ,+3^\circ)$.
    The colour-colour diagram shows the
    position of the main sequence (thin solid line),
    giant stars (thick solid line)
    and the reddening track for an A0V-type star (dashed line)
    based on the \citet{Pickles1998} library of empirical spectra.
    The colour-magnitude only show the reddening vector
    along with the unreddened 1~Gyr isochrone due to \citet{Bressan2012},
    which has been placed at an arbitrary distance of 2~kpc for reference.
    This is one of the least reddened sightlines
    in the survey %(Av XX, Schlegel et al. XXXX)
    and hence the observed stellar population appears to be dominated 
    by lowly reddened main sequence stars.}
    \label{fig:l180}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-45-2.pdf}
        \includegraphics[width=0.5\textwidth]{./plots/cmd-45-2.pdf}
    \end{minipage}
    \caption{Same as above for $(l,b)=(45^\circ,+2^\circ)$,
    which is one of the highest-density sightlines in the survey,
    revealing two groups of stars in colour-magnitude space.}
    \label{fig:l45}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-30-0.pdf}
        \includegraphics[width=0.5\textwidth]{./plots/cmd-30-0.pdf} 
    \end{minipage}
    \caption{Same as above for $(l,b)=(30^\circ,0^\circ)$.
    This is one of the most reddened sightlines in the survey.
    %(XXX, Schlegel et al XXXX).
    }
    \label{fig:l30}
\end{figure*}

\appendix
\input{app_columns.tex}

\section{Candidate emission-line objects towards Sh 2-82}
\label{app:emitters}
\begin{table*}
    \begin{tabular}{lccc}
    \toprule
    Name & $r$ & $i$ & \ha  \\
    \midrule
IPHAS2 J192954.40+181026.1& $17.69\pm0.01$ & $16.12\pm0.01$ & $16.19\pm0.01$ \\
IPHAS2 J193011.01+182051.2& $18.55\pm0.02$ & $16.95\pm0.02$ & $17.31\pm0.02$ \\
IPHAS2 J193021.52+181954.5& $19.72\pm0.05$ & $17.94\pm0.03$ & $18.47\pm0.04$ \\
IPHAS2 J193024.45+181938.3& $19.31\pm0.04$ & $17.55\pm0.02$ & $17.99\pm0.03$ \\
IPHAS2 J193033.00+181609.3& $18.25\pm0.01$ & $16.91\pm0.01$ & $16.92\pm0.01$ \\
IPHAS2 J193042.48+182317.4& $19.96\pm0.03$ & $18.11\pm0.03$ & $18.48\pm0.03$ \\
    \bottomrule
    \end{tabular}
    \caption{Candidate \ha-emitters towards Sh 2-82.}
    \label{tbl:emitters}
\end{table*}

\end{document}\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
%\usepackage{lscape}
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}

\author[G. Barentsen
et. al]{G. Barentsen$^{1}$\thanks{E-mail:geert@barentsen.be},
H. J. Farnhill$^{1}$,
J. E. Drew$^{1}$,
M. J. Irwin$^{4}$, \newauthor
E. A. Gonz$\acute{\rm{a}}$lez-Solares$^{4}$,
R. Greimel$^{2}$,
B. Mizalski$^{3}$,
C. Ruhland$^{1}$, \newauthor plus many friends.
\newauthor\\
$^{1}$Centre for Astrophysics Research, STRI, University of Hertfordshire, College Lane Campus, Hatfield AL10 9AB\\
$^{2}$Institute for Geophysics, Astrophysics and Meteorology, Institute of Physics, Karl-Franzens-Universit$\ddot{a}$t Graz, Universit$\ddot{a}$tsplatz 5, 8010 Graz, Austria\\
$^{3}$Building, Institute, Street Address, City, Code, Country\\
$^{4}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA}

\begin{abstract} % BACKGROUND, OBJECTIVE, METHODS, RESULTS, CONCLUSIONS
The INT/WFC Photometric H$\alpha$ Survey 
of the Northern Galactic Plane (IPHAS)
is a 1800 deg$^2$ imaging survey
covering the entire northern Milky Way at $|b| < 5^\circ$
in the $r$, $i$ and \ha\ filters 
using the Wide Field Camera (WFC) 
on the 2.5-meter Isaac Newton Telescope (INT).
This data release presents the first 
uniformly-calibrated source catalogue
to have been extracted from the survey,
providing single-epoch photometry
for 219 million unique sources
across 92\% of the survey.
The observations were carried out between 2003 and 2012
at a median seeing of 1.1 arcsec
to a depth of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$ and \ha$=20.3\pm 0.3$
($5\sigma$ limits, Vega system).
We explain the data reduction 
and quality control procedures,
describe and test the new uniform photometric calibration,
and detail the construction of the source catalogue
and its quality warning flags.
We find that the new calibration is accurate to
$\sigma=0.03$ mag.
Finally, we demonstrate the ability of the 
catalogue's unique
$r$-$i$/$r$-\ha\ colour-colour diagram to
(i) characterise stellar populations and extinction regimes
towards different Galactic sightlines
and (ii) select reliable candidate \ha-emission line objects.
The catalogue which accompanies this paper
provides the much-needed visible-light counterpart
to several infrared surveys of the Galactic Plane,
including many poorly-studied star-forming regions and ``bubbles'',
and provides images for some of the most
crowded regions to be faced by Gaia.
\end{abstract}

The mean source density as a function of Galactic longitude
is shown in Figure~\ref{fig:density} (thick blue line).
The densities were computed by counting the 
number of sources in $1^\circ$-wide longitude bins
across which covered the entire latitude range $-5^\circ<b<+5^\circ$.
Unsurprisingly, we find the average source densities to increase
towards the Galactic centre.
For example, the average source density near $l\simeq 30^\circ$
is roughly 30\,000 objects per square degree,
which is five times more than the density
found near $l\simeq 180^\circ$.

In addition to the global trend, 
there are significant variations in the source density on smaller scales.
For example,  we find a significant drop near the constellations 
of Cygnus ($l\simeq 80$) and Aquila ($l\simeq 40$),
which are regions known to be affected
by high levels of foreground extinction.
Dark clouds are visible towards these constellation by eye,
and they are often referred to as ``the Great Rift''.

We warn however that the densities reported here 
have not been corrected for survey completeness
or differences in the observing conditions across the survey.
For example, the dip in the density near $l\simeq140^\circ$
is an artificial feature caused by gaps
in the footprint coverage (which are apparent in Fig.~\ref{fig:footprint}).
In a forthcoming paper,
we aim to calibrate the IPHAS-based source densities
by injecting artificial stars into the IPHAS images
and measuring their recovery rate (Farnhill et al., in preparation).
Indeed IPHAS has the potential to offer
calibrated, two-dimensional stellar density maps
which can be used to constrain detailed models of our Galaxy,
but it is beyond the scope of the present work.

In Figure~\ref{fig:density} we also shows the density
of non-blended sources (thin red line).
These are sources for which the \emph{deblend} flag is {\sc false},
i.e. sources for which the CASU pipeline did not have to apply 
a deblending procedure to separate the flux
originating from two or more overlapping objects.
We find a strong correlation between the source density
and the fraction of sources affected by source blending.
For example, only NN\% of the sources are blended
at $l>90^\circ$, whereas NN\% are blended at $l<90^\circ$.

As we explained earlier, blended sources must be used with caution.
Firstly, the deblending-procedure crucially depends
on the local PSF being measured accurately. 
Secondly, blended sources may are likely candidates to have fallen victim
to source confusion during the band-merging procedure.
In future work we hope to investigate the use of
more advanced PSF-fitting routines
in which sources are measured simultaneously across all bands,
perhaps guided by an external list of sources provided
by near-infrared surveys or Gaia data.

@@

\appendix
\input{app_columns.tex}

\section{Candidate emission-line objects towards Sh 2-82}
\label{app:emitters}
\begin{table*}
    \begin{tabular}{lccc}
    \toprule
    Name & $r$ & $i$ & \ha  \\
    \midrule
IPHAS2 J192954.40+181026.1& $17.69\pm0.01$ & $16.12\pm0.01$ & $16.19\pm0.01$ \\
IPHAS2 J193011.01+182051.2& $18.55\pm0.02$ & $16.95\pm0.02$ & $17.31\pm0.02$ \\
IPHAS2 J193021.52+181954.5& $19.72\pm0.05$ & $17.94\pm0.03$ & $18.47\pm0.04$ \\
IPHAS2 J193024.45+181938.3& $19.31\pm0.04$ & $17.55\pm0.02$ & $17.99\pm0.03$ \\
IPHAS2 J193033.00+181609.3& $18.25\pm0.01$ & $16.91\pm0.01$ & $16.92\pm0.01$ \\
IPHAS2 J193042.48+182317.4& $19.96\pm0.03$ & $18.11\pm0.03$ & $18.48\pm0.03$ \\
    \bottomrule
    \end{tabular}
    \caption{Candidate \ha-emitters towards Sh 2-82.}
    \label{tbl:emitters}
\end{table*}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
%\usepackage{lscape}
\usepackage{float}
\usepackage{booktabs}
%\usepackage{aas_macros}

\graphicspath{ {/home/gb/msc/Dropbox/papers/dr2/} }

@@

\author[G. Barentsen
et. al]{Geert Barentsen$^{1}$\thanks{E-mail:geert@barentsen.be},
H. J. Farnhill$^1$,
J. E. Drew$^1$,
E. A. Gonz$\acute{\rm{a}}$lez-Solares$^2$, \newauthor
M. J. Irwin$^2$,
S. E. Sale$^3$,
R. Greimel$^4$,
P. Groot$^5$,
J. Lewis$^2$,
A. Mampaso$^6$, \newauthor
B. Mizalski$^{99}$,
C. Ruhland$^1$,
plus many contributors.
\newauthor\\
$^{1}$School of Physics, Astronomy \& Mathematics, University of Hertfordshire, College Lane, Hatfield, Hertfordshire, AL10 9AB, U.K.\\
$^{2}$Institute of Astronomy, Cambridge University, Madingley Road, Cambridge, CB3 OHA, U.K.\\
$^{3}$Rudolf Peierls Centre for Theoretical Physics, Keble Road, Oxford, OX1 3NP, U.K.\\
$^{4}$IGAM, Institute of Physics, University of Graz, Universit\"atsplatz 5, Graz, Austria.\\
$^{5}$Afdeling Sterrenkunde, Radboud Universiteit Nijmegen, Faculteit NWI, Postbus 9010, 6500 GL Nijmegen, The Netherlands.\\
$^{6}$Instituto de Astrof\'isica de Canarias, 38200 La Laguna, Tenerife, Spain.\\
$^{99}$Please add your current affiliation.\\
}

@@

\begin{abstract} % BACKGROUND, OBJECTIVE, METHODS, RESULTS, CONCLUSIONS
The INT/WFC Photometric H$\alpha$ Survey 
of the Northern Galactic Plane (IPHAS)
is a 1800 square degrees imaging survey
covering the entire northern Milky Way at $|b| < 5^\circ$
in the $r$, $i$ and \ha\ filters 
using the Wide Field Camera (WFC) 
on the 2.5-meter Isaac Newton Telescope (INT).
This data release presents the first 
uniformly-calibrated source catalogue
to have been extracted from the images,
providing single-epoch photometry
for 219 million unique sources
across 92\% of the survey.
The observations were carried out between 2003 and 2012
at a median seeing of 1.1 arcsec
to a depth of $r=21.2\pm 0.5$, $i=20.0\pm 0.3$ and \ha$=20.3\pm 0.3$
($5\sigma$ limits, Vega system).
We explain the data reduction 
and quality control procedures,
describe and test the new uniform photometric calibration,
and detail the construction of the source catalogue
and its quality warning flags.
We find that the new calibration
and the photometric repeatability are accurate to
$\sigma=0.03$~mag.
Finally, we demonstrate the ability of the 
catalogue's unique
$r$-$i$/$r$-\ha\ colour-colour diagram to
(i) characterise stellar populations and extinction regimes
towards different Galactic sightlines
and (ii) select candidate \ha-emission line objects.
The catalogue which accompanies this paper
provides the much-needed visible-light counterpart
to several infrared surveys of the Galactic Plane,
including many poorly-studied star-forming regions and ``bubbles''.
It also provides images for some of the most
crowded regions to be faced by Gaia.
\end{abstract}

@@

The mean source density as a function of Galactic longitude
is shown in Figure~\ref{fig:density} (thick blue line).
The densities were computed by counting the 
number of sources in $1^\circ$-wide longitude bins,
each covering the entire latitude range $-5^\circ<b<+5^\circ$.
Unsurprisingly, we find the average source densities to increase
towards the Galactic centre.
For example, the average source density near $l\simeq 30^\circ$
is roughly 30\,000 objects per square degree,
which is five times more than the density
found near $l\simeq 180^\circ$.

In addition to the global trend, 
there are significant variations
in the source density on smaller scales.
For example,  we find a significant drop near the constellations 
of Cygnus ($l\simeq 80$) and Aquila ($l\simeq 40$),
which are regions known to be affected
by high levels of foreground extinction.
In fact dark clouds are visible towards these constellation by eye,
and they have often been referred to as ``the Great Rift''.

We warn however that the densities reported here 
have not been corrected for survey completeness
or differences in the observing conditions across the survey.
For example, the dip in the density near $l\simeq140^\circ$
is an artificial feature caused by gaps
in the footprint coverage (which are apparent in Fig.~\ref{fig:footprint}).
In a forthcoming paper,
we aim to calibrate the IPHAS-based source densities
by injecting artificial stars into the IPHAS images
and measuring their recovery rate (Farnhill et al., in preparation).
IPHAS has the potential to offer
calibrated, two-dimensional stellar density maps
which can be used to constrain detailed models of our Galaxy.

@@

In Figure~\ref{fig:density} we also shows the density
of non-blended sources (thin red line).
These are sources for which the \emph{deblend} flag is {\sc false},
i.e. sources for which the CASU pipeline did not have to apply 
a deblending procedure to separate the flux
originating from two or more overlapping objects.
We find that the fraction of sources affected by blending problems
is strongly correlated with the local source density.
For example, only 11\% of the sources are blended
at $l>90^\circ$, whereas 24\% are blended at $l<90^\circ$.

As we explained earlier, blended sources must be used with caution.
In particular, we warn that blended sources
are likely candidates to have fallen victim
to source confusion during the band-merging procedure.
In future work we hope to investigate the use of
more advanced PSF-fitting routines
in which sources are measured simultaneously across all bands,
perhaps guided by an external catalogue such as the one
that is to be provided by Gaia.

@@

\appendix
\onecolumn
\section{Catalogue format}
\label{app:columns}

\small
\begin{longtable}{lllp{10cm}}
\caption{\label{tab:columns} 
Definition of columns in the IPHAS DR2 source catalogue.
} \\
\hline
Column & Type & Unit & Description \\
\hline
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued}} \\
\hline
Column & Type & Unit & Description \\
\hline
\endhead

\hline \hline
\endlastfoot
\input{tables/columns.tex}
\end{longtable}
\normalsize
\twocolumn

\section{Candidate emission-line objects towards Sh 2-82}
\label{app:emitters}
\begin{table}
    \begin{tabular}{lccc}
    \toprule
    Name & $r$ & $i$ & \ha  \\
    \midrule
IPHAS2 J192954.40+181026.1& $17.69\pm0.01$ & $16.12\pm0.01$ & $16.19\pm0.01$ \\
IPHAS2 J193011.01+182051.2& $18.55\pm0.02$ & $16.95\pm0.02$ & $17.31\pm0.02$ \\
IPHAS2 J193021.52+181954.5& $19.72\pm0.05$ & $17.94\pm0.03$ & $18.47\pm0.04$ \\
IPHAS2 J193024.45+181938.3& $19.31\pm0.04$ & $17.55\pm0.02$ & $17.99\pm0.03$ \\
IPHAS2 J193033.00+181609.3& $18.25\pm0.01$ & $16.91\pm0.01$ & $16.92\pm0.01$ \\
IPHAS2 J193042.48+182317.4& $19.96\pm0.03$ & $18.11\pm0.03$ & $18.48\pm0.03$ \\
    \bottomrule
    \end{tabular}
    \caption{Candidate \ha-emitters towards Sh 2-82.}
    \label{tbl:emitters}
\end{table}
